%
% AplotCLoptions.tex
%
% Command-Line Options for "gff2aplot".
%
% # $Id: AplotCLoptions.tex,v 1.2 2001-09-06 18:33:36 jabril Exp $
%
% \newcommand{\op}[1]{\bfseries\sffamily #1}
% \newcommand{\tp}[1]{'{\bfseries\sffamily #1}'}
% \newcommand{\pr}[1]{\mdseries\sffamily\slshape $<$#1$>$}
% \newcommand{\x}{\textmd{\,,\,}}
%
\newcommand{\cltitem}[4]{
  \item[\op{#1 \pr{#2}}]\hfill\op{#3}=\op{#4}\\[1ex]
  }
\newcommand{\clpitem}[3]{
  \item[\op{#1 \pr{#3}}]\hfill\op{#2}=\pr{#3}\\[1ex]
  }
\newcommand{\clsitem}[3]{
  \item[\op{#1}]\hfill\op{#2}=\op{#3}\\[1ex]
  }
\newcommand{\clritem}[1]{
  \item[\op{#1}]\ \\[1ex]
  }
\newcommand{\clmitem}[1]{
  \item[\op{\shortstack[l]{\ #1}}]\ \\[1ex]
  }
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{description}
\clmitem{-v\\-\/-verbose}
By default, warnings and errors are sent to standard error. This option 
switches on process reporting messages to appear on standard error too.
\clmitem{-V \pr{logs\_filename}\\-\/-logs-filename \pr{logs\_filename}}
If is possible to open '\pr{logs\_filename}' then such file will contain 
all the messages and warnings produced by the program even though they 
will be disabled from standard error with \tp{-\/-quiet} option.
\clmitem{-q\\-\/-quiet}
This option disables any message or warning from standard error. It does not 
disable error report because such errors are pointing a problem which can 
make {\prog} produce unexpected results. Solve the cause of such problems 
before continuing to run the program in a silent mode. 
\clmitem{-\/-feature-var '\pr{feature::variable=value}'}
Loading a customization variable for a GFF feature element from command-line. % '\pr{custom\_file}'. 
\clmitem{-\/-group-var '\pr{group::variable=value}'}
Loading a customization variable for a GFF group element from command-line. % '\pr{custom\_file}'. 
\clmitem{-\/-strand-var '\pr{strand::variable=value}'}
Loading a customization variable for a GFF strand element from command-line. % '\pr{custom\_file}'. 
\clmitem{-\/-source-var '\pr{source::variable=value}'}
Loading a customization variable for a GFF source element from command-line. % '\pr{custom\_file}'. 
\clmitem{-\/-sequence-var '\pr{sequence::variable=value}'}
Loading a customization variable for a GFF sequence element from command-line. % '\pr{custom\_file}'. 
\clmitem{-\/-layout-var '\pr{variable=value}'}
Loading a customization variable for page layout from command-line. % '\pr{custom\_file}'. 
\clmitem{-O \pr{custom\_filename}\\-\/-custom-filename \pr{custom\_filename}}
Loading customization parameters from '\pr{custom\_file}'. Now you can load several customization files by passing this option several times. The precedence is the input order in the command-line, so, for the common definitions, the last '\pr{custom\_file}' will override previous '\pr{custom\_files}' settings.
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\clmitem{}
\end{description}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
